Figure 3. Tissue Microbiome Abundances

### 2022-02-10 reports/rmarkdown/manuscript/Figure3.Rmd
Save pdf image to common folder

---
title: "Figure 3. Tissue Microbiome Abundances"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

# m <- metadata %>%
#   select(ID, Luminal_gr, Tissue_gr) %>%
#   left_join(div, by="ID") %>%
#   arrange(Tissue_gr) %>%
#   group_by(Tissue_gr) %>%
#   nest() %>%
#   mutate(L = map(data, ~arrange(.x, Luminal_gr, Shannon))) %>%
#   unnest(L)

# metadata <- metadata %>%
#   arrange(factor(ID, levels = m$ID))

@@

```{r Figure 3., echo=FALSE, warning=FALSE, message=FALSE,  fig.pos="t"}
#  fig.width=6 ,fig.asp=1, fig.height=7,
### A
#############################
# DIVERSITY + TAX ABUNDANCE #
#############################
figlabels <- letters

>>>>

---
title: "Figure 3. Tissue Microbiome Abundances"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}

##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

@@

```{r Figure 3, echo=FALSE, warning=FALSE, message=FALSE, fig.width=6, fig.pos="t"}
# fig.asp=1, fig.height=7,
### A
#############################
# DIVERSITY + TAX ABUNDANCE #
#############################
figlabels <- letters
